%-------------------------
% Resume in Latex
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage{fontawesome5}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[super]{nth}
\usepackage{booktabs}
\usepackage{accsupp}
\usepackage{xifthen}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
% defines one's email
% usage: \email{<email>}
\newcommand{\email}[1]{\faEnvelope\ \href{mailto:#1}{#1}}
% defines one's phone
% usage: \phone{<phone>}
\newcommand{\phone}[1]{\faPhone\ {#1}}
% defines one's linkedin
% usage: \linkedin{<linkedin>}
\newcommand{\linkedin}[1]{\href{#1}{\faLinkedin}}
% defines one's GitHub
% usage: \github{<github>}
\newcommand{\github}[1]{\href{#1}{\faGithub}}

% defines one's homepage
% usage: \homepage{<homepage>}
\newcommand{\homepage}[2][]{\faLink\ 
  \ifthenelse{\isempty{#1}}%
    {\href{#2}{#2}}
    {\href{#2}{#1}}}
\newcommand{\researchgate}[1]{\href{#1}{\faResearchgate}}
\newcommand{\orcid}[1]{\href{#1}{\faOrcid}}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\link}[2]{\href{#1}{\color{blue}\underline{#2}}}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newenvironment{resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}{\end{itemize}}
\newenvironment{resumeItemList}{\begin{itemize}}{\end{itemize}}
\newenvironment{resumeItemSubList}{\begin{itemize}\setlength\itemsep{0.4em}}{\end{itemize}\vspace{-5pt}}

\newcommand{\awardsTable}[1]{
	\begin{tabularx}{\textwidth}{llllll}
	\emph{Name}	& \emph{Placing}	& \emph{Scope}	& \emph{Awarder} & \emph{Year}       \\
	\midrule\midrule
	#1
	\end{tabularx}
}
\newcommand{\awardsTableRow}[6]{
	\BeginAccSupp{method=plain, ActualText=11\string\t 21}#1 & #2 & #3 & #4 & #5\EndAccSupp{} \\
}

\fancyfoot[L]{
  \small \LaTeX\ Source: \link{https://github.com/vectorsss/cv}{github.com/vectorsss/cv} $|$ 
  Web Version: \link{https://cv.zhaochi.ru}{cv.zhaochi.ru}
}

\renewcommand\footrule{\hrule width\textwidth}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\begin{center}
  \begin{flushright}
    \footnotesize{\it Compiled on \today{}.}
  \end{flushright}
\end{center}
\begin{center}
  \textbf{\huge \scshape Chi Zhao (Vector)} \\ \vspace{1pt}
  \small \email{vector.zhaochi@gmail.com} $|$ \homepage[https://chizhao.gitlab.io]{https://chizhao.gitlab.io} $|$ \linkedin{https://www.linkedin.com/in/dandanv5} $|$ \github{https://github.com/vectorsss} $|$
  \researchgate{https://www.researchgate.net/profile/Chi-Zhao-4} $|$ \orcid{https://orcid.org/0000-0002-1166-7578}
\end{center}

\section{Education}
\begin{resumeSubHeadingList}
  \resumeSubheading
    {Saint Petersburg State University}{Sept. 2021 -- Jun. 2025}
    {PhD in Applied Mathematics and Control Processes}{Saint Petersburg, Russia}
    \resumeSubSubheading
    {Thesis Title: ``Modeling of binary opinion dynamics in social networks of complex configurations''}{Defended in Apr. 2025}

  \resumeSubheading
    {Saint Petersburg State University}{Sept. 2019 -- Jun. 2021}
    {M.S. in Applied Mathematics and Informatics (GPA: 4.9/5.0)}{Saint Petersburg, Russia}

  \resumeSubheading
    {Beijing Institute of Technology}{Jul. 3 -- 28, 2017}
    {ACM Summer Camp}{Beijing, China}

  \resumeSubheading
    {Yanan University}{2015 -- 2019}
    {B.S. in Computer Science (GPA: 3.1/4.0)}{Yanan, China}
\end{resumeSubHeadingList}

\section{Working Experience}
\begin{resumeSubHeadingList}

  \resumeSubheading
    {Huawei Inc.}{Sep. 2021 -- Present}
    {R\&D Engineer}{Saint Petersburg, Russia}
  \resumeSubheading
    {Wisedu Inc.}{Sep. 2016 -- May. 2019}
    {Software Engineer}{Yanan, China}
    % \resumeSubheading {Semi-decentralized of Blockchain Technology}{May 2019
    % -- Aug. 2019} {Blockchain Developer}{Yanan, China} \begin{resumeItemList}
    % \resumeItem{Implemented the core algorithm of the blockchain.}
    % \resumeItem{Proposed theoretical improvements on the shortcomings of the
    % current blockchain.} \resumeItem{Developed a material tracking system
    % based on Semi-decentralized Blockchain.} \end{resumeItemList}

    % \resumeSubheading {Fast calculation of massive high dimensional vector
    % similarity}{May 2018 -- Aug. 2018} {Algorithm Engineer}{Yanan, China}
    % \begin{resumeItemList} \resumeItem{Realized preprocessing of large data
    % under small memory computer conditions.} \resumeItem{Implemented PCA
    % dimensionality reduction algorithm.} \resumeItem{Developed Nearest
    % Neighbor Algorithm using Ball-Tree.} \end{resumeItemList}

    % \resumeSubheading {Online news classification system based on CNN}{Mar.
    % 2018 -- May. 2018} {Full Stack Engineer}{Yanan, China}
    % \begin{resumeItemList} \resumeItem{Developed a web crawler to get Netease
    % News in real time and store it in a database.} \resumeItem{Implemented
    % Chinese text classification algorithm using CNN.} \resumeItem{Developed
    % the interaction between the front end and the back end of the project.}
    % \end{resumeItemList}

\end{resumeSubHeadingList}
\section{Project Experience}
\begin{resumeSubHeadingList}
  \resumeSubheading
    {* Professional model data governance/Valuable training data selection}{2025}
    {Project leader}{Saint Petersburg, Russia}
    \resumeSubSubheading{Project focused on improving model performance through data governance and optimized feature/training data selection.}{}
    \resumeSubSubheading{Sampled 60M representative records from 1.8B wireless data using custom diversity sampling algorithms.}{}
    \resumeSubSubheading{Boosted model accuracy by 22\% using custom sampling and anomaly detection algorithms.}{}
    \resumeSubSubheading{Accelerated training by 10\% via custom feature importance algorithms that removed 20\% redundant features.}{}
  \resumeSubheading
    {* Internal columnar storage algorithm}{2023--2024}
    {R\&D Engineer}{Saint Petersburg, Russia}
    \resumeSubSubheading{High-performance, highly flexible columnar storage lossless compression algorithm}{}
    \resumeSubSubheading{The algorithm will be commercialized to store base station data.}{}
    \resumeSubSubheading{LTE (4G) data 30\% CR, NR (5G) data 40\% CR, without loss any performance.}{}
  \resumeSubheading
    {Russian Science Foundation Grant \link{https://rscf.ru/en/project/22-21-00346/}{No. 22-21-00346}}{2023}
    {Researcher}{Saint Petersburg, Russia}
    \resumeSubSubheading{Completed simulation of two-layer opinion dynamics models, focusing on expressed and private opinions.}{}
  \resumeSubheading
    {* Elastic expansion algorithm for internal distributed file storage systems}{2023}
    {R\&D Engineer}{Saint Petersburg, Russia}
    \resumeSubSubheading{Enabled seamless HOFS multi-node expansion using HRW Hashing with minimal data movement and no performance loss.}{}
    \resumeSubSubheading{Improved system reliability by ensuring data access continuity even after hash ring loss.}{}
  \resumeSubheading
    {* Packet/Router data compression}{2023}
    {R\&D Engineer}{Saint Petersburg, Russia}
    \resumeSubSubheading{This project achieved 85\% CR without loss (Save 7x disk usage).}{}
  \resumeSubheading
    {* Wireless data compression}{2021--2022}
    {R\&D Engineer}{Saint Petersburg,Russia}
    \resumeSubSubheading{This project achieved 96\% CR through lossy compression.}{}
  \resumeSubheading
    {* SparkSQL query optimization}{2021}
    {R\&D Engineer}{Saint Petersburg, Russia}
    \resumeSubSubheading{This project speeds up query execution by 50\% through predicate pushdown and optimization of data structures.}{}
    % \resumeSubheading {Fast calculation of massive high dimensional vector
    % similarity}{May 2018 -- Aug. 2018} {Algorithm Engineer}{Yanan, China}
    % \resumeSubSubheading{This project improves the efficiency of the nearest
    % neighbor algorithm and won the \nth{3} prize in the China Software Cup
    % 2018.}{} \newpage \resumeSubheading {Online news classification system
    % based on CNN}{Mar. 2018 -- May. 2018} {Full Stack Engineer}{Yanan, China}
    % \resumeSubSubheading{This project has obtained a Chinese software
    % registration certificate.}{} \resumeSubSubheading{This project won the
    % \nth{3} prize in the Computer Design Competition 2018.}{}
\end{resumeSubHeadingList}

\newpage
%-----------PROJECTS-----------
\section{Patent / Copyright Certificates}
\begin{resumeSubHeadingList}
  \resumeSubheading
    {A program for modeling the opinion dynamics in two-layer networks}{2023}
    {Russian Computer Software Copyright Registration Certificate}{{\link{https://new.fips.ru/registers-doc-view/fips_servlet?DB=EVM&DocNumber=2023661532&TypeFile=html}{NO. 2023661532}}}
  \resumeSubheading
    {Online News Classification System Based on Convolutional Neural Network}{2018}
    {Chinese Computer Software Copyright Registration Certificate}{NO. 2831192}
\end{resumeSubHeadingList}

\section{Open Source Projects}
\begin{resumeSubHeadingList}

  \resumeProjectHeading{
    \link{https://github.com/vectorsss/shapG}{\textbf{ShapG}} $|$
    \emph{python $\cdot$ feature importance algorithm $\cdot$ centrality
          measures}}{}
  \begin{resumeItemList}
    \resumeItem{A Python package for feature importance algorithms based on
                Shapley values.}
    \resumeItem{This package can also be used to calculate the centrality in
                the graph.}
  \end{resumeItemList}
  \resumeProjectHeading{
    \link{https://github.com/vectorsss/news_classification}{\textbf{News
        Classification}} $|$
    \emph{python $\cdot$ NLP $\cdot$ CNN $\cdot$ text classification}}{}
  \begin{resumeItemList}
    \resumeItem{Online News Classification System Based on Convolutional Neural
                Network.}
    \resumeItem{This project was awarded the provincial \nth{3} prize in the
                2018 national computer design competition.}
  \end{resumeItemList}
\end{resumeSubHeadingList}

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Programming}{: Python $\cdot$ C/C++ $\cdot$ Go $\cdot$ Rust $\cdot$ Matlab/Octave $\cdot$ Julia $\cdot$ R $\cdot$ SQL $\cdot$ \LaTeX} \\
        \textbf{ML Libraries}{: Tensorflow $\cdot$  PyTorch $\cdot$ Keras $\cdot$  Scikit-Learn} \\
        \textbf{Developer Tools}{: Git $\cdot$ Docker $\cdot$  Google Cloud Platform} \\
        \textbf{OS}{: Windows $\cdot$ MacOS $\cdot$ Arch Linux} \\
        \textbf{Languages}{: Chinese (native), and English (professional working proficiency)}
        }}
\end{itemize}

\section{Research interests}
\begin{resumeSubHeadingList}
  \resumeProjectHeading{
    Graph Algorithms $\cdot$ Centrality Measures $\cdot$ Machine learning
    $\cdot$ Explainable Artificial Intelligence $\cdot$ Probability Theory
    $\cdot$ Statistics}{}
  \resumeProjectHeading{
    Data Compression $\cdot$ Coding Theory $\cdot$ Time Series Analysis $\cdot$
    Optimization $\cdot$ Stochastic Modeling $\cdot$ Stochastic Processes}{}
\end{resumeSubHeadingList}
\section{Teaching}
\begin{resumeSubHeadingList}
  \resumeSubheading{Applied Statistics in R}{Saint-Petersburg, Russia}{Teaching
                    assistant}{2024}
  \resumeSubheading{Statistical Decisions and Econometrics}{Saint-Petersburg,
                    Russia}{Teaching assistant}{2022}
\end{resumeSubHeadingList}
\section{Community service}
\begin{resumeSubHeadingList}
  \resumeProjectHeading{{\bf Reviewer for journals and conferences}}{}
  \begin{resumeItemList}
    \resumeItem{Engineering Applications of Artificial Intelligence (EAAI)}
    \resumeItem{International Conference On Computational Optimization (ICOMP)}
  \end{resumeItemList}
\end{resumeSubHeadingList}
\section{Selected Publications}
\begin{enumerate}
  \fontsize{10}{10.5}\selectfont
  \item [1.] \textbf{Zhao C.}, Liu J., Parilina E. M. Complete-to-Sparse: A Novel Graph Construction Strategy for Efficient ShapG // {\it Mathematical Optimization Theory and Operations Research}. -- Cham : Springer Nature Switzerland. -- 2025. -- P. 180–194.
  \item [2.] \textbf{Zhao C.}, Liu J., Parilina E. M. ShapG: new feature importance method based on the Shapley value // {\it Engineering Applications of Artificial Intelligence.} -- 2025. -- May. -- Vol. 148, 110409. {\bf (Q1, IF: 8.0)}
  \item [3.] \textbf{Zhao C.}, Parilina E. M. Centrality measures and opinion dynamics in two-layer networks with replica nodes // {\it Computers and Operations Research.} -- 2026. -- Jan. -- Vol. 185, 107245. {\bf (Q1, IF: 4.3)}
  \item [4.] \textbf{Zhao C.}, Parilina E. M. Analysis of consensus time and winning rate in two-layer networks with hypocrisy of different structures // {\it Vestnik of Saint Petersburg University. Applied Mathematics. Computer Science. Control Processes.} -- 2024. -- Vol. 20, no. 2. -- P. 170-192.
  \item [5.] \textbf{Zhao C.}, Parilina E. M. Opinion Dynamics in Two-Layer Networks with Hypocrisy // {\it Journal of the Operations Research Society of China}. -- 2024. -- Mar. -- Vol. 12, no. 1. -- P. 109-132. {\bf (Q2)}
  \item [6.] \textbf{Zhao C.}, Parilina E. M. Network Structure Properties and Opinion Dynamics in Two-Layer Networks with Hypocrisy // {\it Mathematical Optimization Theory and Operations Research}. -- Cham : Springer Nature Switzerland. -- 2024. -- P. 300-314.
  \item [7.] \textbf{Zhao C.}, Parilina E. M. Consensus time and winning rate based on simulations in two-layer networks with hypocrisy // {\it 2023 7th Scientific School Dynamics of Complex Networks and their Applications (DCNA).} -- 2023. -- P. 68-71.
\end{enumerate}

\section{Conferences}
\begin{resumeSubHeadingList}
  \resumeSubheading{Mathematical Optimization Theory and Operations Research
                    (MOTOR 2025)}{Novosibirsk, Russia}{Oral Presentation}{July.
                    07 - 11, 2025}
  \resumeSubheading{Game Theory and Management (GTM 2025)}{Saint-Petersburg,
                    Russia}{Oral Presentation}{July. 2 - 4, 2025}
  \resumeSubheading{\nth{14} International Society of Dynamic Games (ISDG) Workshop}{Yerevan, Armenia}{Oral Presentation}{June. 11 - 13, 2025}
  \resumeSubheading{International Conference On Computational Optimization
                    (ICOMP 2024)}{Innopolis, Russia}{Visitor}{Oct. 10 - Oct.
                    12, 2024}
  \resumeSubheading{Mathematical Optimization Theory and Operations Research
                    (MOTOR 2024)}{Omsk, Russia}{Oral Presentation}{June. 30 -
                    July. 06, 2024}
  \resumeSubheading{Game Theory and Management (GTM 2024)}{Saint-Petersburg,
                    Russia}{Oral Presentation}{June. 26 - 28, 2024}
  \resumeSubheading{Dynamics of Complex Networks and their Applications (DCNA
                    2023)}{Kaliningrad, Russia}{Poster Presentation}{Sep. 18 -
                    20, 2023}
  \resumeSubheading{Game Theory and Management (GTM 2023)}{Saint-Petersburg,
                    Russia}{Oral Presentation}{June. 28 - 30, 2023}
  \resumeSubheading{Control Processes and Stability 2022}{Saint-Petersburg,
                    Russia}{Oral Presentation}{Apr. 4 - 8, 2022}
  \resumeSubheading{Control Processes and Stability 2021}{Saint-Petersburg,
                    Russia}{Oral Presentation}{Apr. 5 - 9, 2021}
  \resumeSubheading{The Computing Conference 2017}{Hangzhou,
                    China}{Visitor}{Oct. 11 - 14, 2017}
  \resumeSubheading{Yiban Developer Conference 2017}{Shanghai,
                    China}{Developer}{Aug. 2017}
  \resumeSubheading{Language \& Intelligence Summit 2017}{Beijing,
                    China}{Visitor}{July 23, 2017}
\end{resumeSubHeadingList}

\section{Honours \& Awards}
\setlength{\tabcolsep}{6.0pt}
\renewcommand{\arraystretch}{1.1}
\fontsize{8.5}{11}\selectfont
\awardsTable{
  \awardsTableRow{General Development Star}{-}{Huawei Inc.}{General development
                  department}{Oct. 2024} \\
  \awardsTableRow{General Development Star}{-}{Huawei Inc.}{General development
                  department}{Jun. 2023} \\
  \awardsTableRow{General Development Star}{-}{Huawei Inc.}{General development
                  department}{Oct. 2022} \\
  \awardsTableRow{President's Award (Team)}{-}{Huawei Inc.}{MAE-M
                  department}{Dec. 2021} \\
  \awardsTableRow{Diploma with distinction}{-}{University}{Saint Petersburg
                  State University}{Jun. 2021} \\
  \awardsTableRow{Excellent Graduation Thesis (Design)}{-}{University}{Yanan
                  University}{Jun. 2019} \\
  \awardsTableRow{Excellent Graduate}{-}{University}{Yanan University}{Jun.
                  2019} \\
  \awardsTableRow{Merit Student Scholarship}{-}{University}{Yanan
                  University}{Dec. 2018} \\
  \awardsTableRow{China Software Cup Competition}{\nth{3}}{China}{China
                  Software Cup Organizing Committee}{Oct. 2018} \\
  \awardsTableRow{Computer Design Competition}{\nth{3}}{Northwest
                  China}{Northwest University (China)}{May. 2018} \\
  \awardsTableRow{Mathematical Contest in Modeling}{\nth{2}}{Shaanxi}{China
                  Society for Industrial and Applied Mathematics}{Dec. 2017} \\
  \awardsTableRow{Mathematics Competition}{\nth{3}}{Shaanxi}{Chinese
                  Mathematical Society}{Nov. 2016} \\ \hline }

\end{document}

